---
title: "Progress Overview"
#date: `r format(Sys.time())`
output: html_document
---
```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(osfr)
##osf_auth(token = "D:/osf-token.txt")
#library(flexdashboard)

# List the sequential output of each lab
lab_seq <- dir(path = "..",pattern = "Seq_output.csv",recursive = TRUE,full.names = TRUE)

# Get the latest lab tracking information
csv_path <- dir(path="..",recursive = TRUE, pattern = "Lab_info.csv", full.names = TRUE)

# Function of plotting sequential analysis
seq_plot <- function(data){
  ## Draw results of sequential analysis
  with(data, plot(N,BF, type = "b", xlab = "Sample Size", 
                        ylab = "Bayes Factor", ylim = c(-30, 30), pch = 19, 
                        col = "gray48", lwd = 2))
  abline(h = 0, lwd = 1)
  abline(h = 10, col = "black", lty = 2, lwd = 2)
  abline(h = -10, col = "black", lty = 2, lwd = 2)
  text(0, 7 + 0.4, labels = "Evidence for Alternative", 
       cex = 1.5, col = "black", pos = 4)
  text(0, -7 - 0.4, labels = "Evidence for Null", 
       cex = 1.5, col = "black", pos = 4)
  abline(v = 50, col = "red", lwd = 1)
}

```

### Latest Update
`r format(Sys.time(),usetz = TRUE)`

### For Participant Laboratories
- Check the [steps manual](https://docs.google.com/document/d/1XFj9qQT500lAEe3fjGNab6TTU_lgUWTiWWSh8oF3jGE/edit?usp=sharing); download the latest OpenSesame Scripts at [Project OSF](https://osf.io/e428p/).
- Navigate the tracking logs and enter the language page you are testing. There is the link to 003 survey page on the top. The sequential analysis plot for a lab will be available when a lab has collected 50 participants.

### Information Board

Column names explain:

- **PSA_ID**: Lab ID in Psychological Science Accelerator
- **N**: Maximal sample size this lab will recruit
- **Seq_N**: Sample Size to initialize the sequential analysis after 50.
- **osfid**: OSF repository for collected data
- **Language**: Primary language this lab is testing
- **Publicity**: Is this repository public?
- **log**: Is Lab log available?

```{r lab_osf, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}

info <- read.csv(csv_path) %>% subset(N!=0)
info$log <- rep("No",length(info$osfid))
for(i in 1:length(info$osfid)){
  if(info$Publicity[i] == "Yes"){
      cr_project <- osf_retrieve_node(as.character(info$osfid[i]))
     info$log[i] <- ifelse((cr_project %>% osf_ls_files() %>%
                 select("name") %>%
                 dim())[1]>0,"Yes","No") 
  }
}
knitr::kable(info[-1], caption = "Labs planned N.")
```

