---
title: "Progress Overview"
#date: `r format(Sys.time())`
output: html_document
---
```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(osfr)
##osf_auth(token = "D:/osf-token.txt")
#library(flexdashboard)

# List the sequential output of each lab
lab_seq <- dir(path = "..",pattern = "Seq_output.csv",recursive = TRUE,full.names = TRUE)

# Get the latest lab tracking information
lab_info_path <- dir(path="..",recursive = TRUE, pattern = "Lab_info.csv", full.names = TRUE)

# Get the available log data
lab_fin_path <- dir(path="..",recursive = TRUE, pattern = "lab_fin.csv", full.names = TRUE)

# Get the available rawdata of verification task
rawdata_V_path <- dir(path="..",recursive = TRUE, pattern = "rawdata_SP_V.csv", full.names = TRUE)


# Function of plotting sequential analysis
seq_plot <- function(data){
  ## Draw results of sequential analysis
  with(data, plot(N,log(BF,10), type = "b", xlab = "Sample Size", 
                        ylab = "(log)Bayes Factor(10)", ylim = c(-2.5, 2.5), pch = 19, 
                        col = "gray48", lwd = 2))
  abline(h = 0, lwd = 1)
  abline(h = log(10,10), col = "black", lty = 2, lwd = 2)
  abline(h = log(1/10,10), col = "black", lty = 2, lwd = 2)
  text(0, log(10,10) + 0.4, labels = "Evidence for Alternative", 
       cex = 1.5, col = "black", pos = 4)
  text(0, log(1/10,10) - 0.4, labels = "Evidence for Null", 
       cex = 1.5, col = "black", pos = 4)
  abline(v = 50, col = "red", lwd = 1)
}

```

### Latest Update
`r format(Sys.time(),usetz = TRUE)`

### For Participant Laboratories
- Check the [steps manual](https://docs.google.com/document/d/1XFj9qQT500lAEe3fjGNab6TTU_lgUWTiWWSh8oF3jGE/edit?usp=sharing); download the latest OpenSesame Scripts at [Project OSF](https://osf.io/e428p/).
- Navigate the tracking logs and enter the language page you are testing. There is the link to 003 survey page on the top. The sequential analysis plot for a lab will be available when a lab has collected 50 participants.

### Information Board

Column names explain:

- **PSA_ID**: Lab ID in Psychological Science Accelerator
- **N**: Maximal sample size this lab will recruit
- **Seq_N**: Sample Size to initialize the sequential analysis after 50.
- **osfid**: OSF repository for collected data
- **Language**: Primary language this lab is testing
- **Publicity**: Is this repository public?
- **collected_N**: Number of collected participants
- **begin_date**: First date and time this lab collected the data
- **latest_date**: Latest date and time this lab collected the data
- **Finish**: '*' represents the labratories that finished the data collection prior to the latest updated date.
<!---
- **log**: Is Lab log available?
--->

```{r lab_osf, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
require(lubridate)

info <- read.csv(lab_info_path) %>% subset(N!=0) %>% 
  left_join(
read.csv(rawdata_V_path) %>% 
  group_by(PSA_ID) %>% 
  ##group_by(SEED) %>%
  summarise(collected_N = length(unique(subject_nr)), 
          begin_date = min(parse_date_time(datetime,orders = c('mdy HMS','b d HMS Y')) %>%
                       ##min(parse_date_time(DATE,orders = c('dmy','mdy','ymd','dmy, h.m','ymd, h:m')) %>%
                    format(format="%Y-%m-%d")), 
          lastest_date = max(parse_date_time(datetime,orders = c('mdy HMS','b d HMS Y','a b d HMS Y')) %>%
                       ##max(parse_date_time(DATE,orders = c('dmy','mdy','ymd','dmy, h.m','ymd, h:m')) %>%
                               format(format="%Y-%m-%d"))), 
   by="PSA_ID"
)

lab_fin <- read.csv(lab_fin_path)
info <- data.frame(info, Finish = ifelse(info$PSA_ID %in% lab_fin$PSA_ID, "*",""))
##info$log <- rep("No",length(info$osfid))
##for(i in 1:length(info$osfid)){
##  if(info$Publicity[i] == "Yes"){
##      cr_project <- osf_retrieve_node(as.character(info$osfid[i]))
##     info$log[i] <- ifelse((cr_project %>% osf_ls_files() %>%
##                 select("name") %>%
##                 dim())[1]>0,"Yes","No") 
##  }
##}
knitr::kable(info[-1], caption = "Labs planned N and progress.")
```

